CodeBook
========
Description of tidy data files

## Tidy data set 1
To read the file do
`
read.table("tidyData1.txt", header=TRUE)
`

```{r}
df <- read.table("tidyData1.txt", header=TRUE)
str(df)
```

## Tidy data set 2
To read the file do
`
read.table("tidyData2.txt", header=TRUE)
`

The data frame contains one line per combination of `activity` and `subject` which is the mean
of the observations in this subset in tidy data set 1.

```{r}
df2 <- read.table("tidyData2.txt", header=TRUE)
str(df2)
```


## Explanation of Variables

### subject  
The identifier of the experimental subject. It is in the range `r min(df$subject)` to 
`r max(df$subject)`.

### activity  
The activity that the subject was engaged in while the measurements were taken. Possible value are:
```{r, echo=FALSE, results='asis'}
cat("\n", levels(df$activity), sep="\n - ")
```

### dataSet  
The data set that the subject was part of. Possible value are:
```{r, echo=FALSE, results='asis'}
cat("\n", levels(df$dataSet), sep="\n - ")
```

### measurement variables
These correspond to a subset of the raw daw data variables but with slightly modified names. 
In particular only those measurements which contain the text `mean`,`Mean`,`std` or `Std` 
are retained.   
The names are also modified so as to remove characters that are illegal in R and to make their
reading slightly easier. The modifications performed are:
 - Removal of `()`
 - Removal of `-`
 - Capitalisation of the first letter of `mean` or `std`.
 
For example `tBodyAcc-mean()-X` becomes `tBodyAccMeanX`, etc.

The actual meaning of these variables can be found in the original `features_info.txt` file.
